### 2021-02-24 introduction.tex
prelim scanned

Our recommender uses a graph convolutional neural network \cite{kipf2017semisupervised}
to represent the problem structure. It learns from the ATP performance on selected problems
and pairs of randomly sampled precedences. This information is then used to train
a \emph{symbol cost model}, which realizes the recommendation by simply sorting 
the problem's symbols according the obtained costs.

>>>>

Our recommender uses a graph convolutional neural network \cite{kipf2017semisupervised}
to represent the problem structure. It learns from the ATP performance on selected problems
and pairs of randomly sampled precedences. This information is used to train
a \emph{symbol cost model}, which then realizes the recommendation by simply sorting 
the problem's symbols according the obtained costs.

### 2021-02-24 preliminaries.tex
Remove a resolved todo
prelim scanned

% Terminology

\todo[inline,author=FB]{Get inspiration from PAAR paper.}

@@

@@

The \gls{sot} influences the superposition calculus in two ways.
First, the inferences on each clause are limited
to the selected literals.
\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
In each clause,
either a negative literal or all the maximal literals are selected.
The maximality is evaluated
according to the simplification ordering.
% Note: The selection function Total does not use the simplification ordering.
Second, the simplification ordering orients some of the equalities
to prevent superposition and equality factoring
from inferring redundant complex conclusions.
In each of these two roles,
the simplification ordering may impact the direction and,
in effect, the length of the proof search.

The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation of the non-logical symbols of the input problem.
In this work we focus on finding a symbol precedence achieves a good performance when plugged into the \gls{kbo},
leaving all the symbol weights at the default value 1 as set by the \gls{atp} \Vampire{}.

@@

A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
Each of the components of the output vector is called a \emph{unit} of the module.
The output of each module is differentiable with respect to the input.

@@

>>>>

@@

\todo{MS: Celkove hezky! Jen mi tu nejak chybi konec... A taky proc se to vsechno rika.
V PAAR clanku, pokud si dobre vzpominam, bylo hlavnim cilem zavest znaceni pro
 ``pocet iteraci nez se najde dukaz''. aby se pak pouzilo dale\dots
Nicmene ctu ted beginning->end, tak nevim, co chystas dale. }

@@

The \gls{sot} influences the superposition calculus in two ways.
First, the inferences on each clause are limited
to the selected literals.
\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
\todo{MS: the original paper is \cite{DBLP:journals/logcom/BachmairG94}. 
Stoji za precteni, at se v tom trochu vyznas!
Mimochodem, mozna ze ``simplification ordering'' neni ten uplne nejpresnejsi nazev. 
Pripadne na ten clenek mrkni rychle uz ted. V tehle sekci by se hodily nejake citace,
aby bylo jasne, od koho terminy prejimame.
(Weidenbachova kapitola v Handbooku taku (Combining superposition, sorts and splitting)
taky tusim definuje presne vlastnosti toho usporadani a dava jim jmeno.}
In each clause,
either a negative literal or all the maximal literals are selected.
The maximality is evaluated
according to the simplification ordering.
% Note: The selection function Total does not use the simplification ordering.
\todo{MS: Ta logika je (pro pripomenuti):
1) pravidla jsou sound i bez restrikci, (proto selection Total je v pohode)
2) nicmene se ukazuje, ze cim mene toho selectem a tedy cim mene bude provedeno inferenci, tim lepe typicky pro search (vetsi sance dokazat (i tezke) problemy)
3) na treti stranu, nemuzem nedelat nic - to by nebylo complete.
4) Pravidla o selekci literalu, ktera popisujes, vyjadruji
minimalni selekci, o ktere se podarilo dokazat (BachmairGanzinger), ze zaruci uplnost. 
}
Second, the simplification ordering orients some of the equalities
to prevent superposition and equality factoring
from inferring redundant complex conclusions.
In each of these two roles,
the simplification ordering may impact the direction and,
in effect, the length of the proof search.

The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation of the non-logical symbols of the input problem.
In this work we focus on finding a symbol precedence which 
leads to a good performance of an ATP
when plugged into the \gls{kbo},
leaving all the symbol weights at the default 
value 1 as set by the \gls{atp} \Vampire{}.

@@

A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
Each of the components of the output vector is called a \emph{unit} of the module.
The output of each module is differentiable with respect to the input.
\todo{MS: mozna bych byl opetrnejsi. Co ReLU a derivace v bode zlomu? ;)}

@@

\todo{MS: Hezke! Ted uz v arichtekture muzes mavat pojmy o neuronkach a bude to tu uktovne! }
